---
title: "MUSA 508 Assignment 4"
author: "Leah Shapiro and Palak Agarwal"
date: "10/28/2020"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
 
---
# Introduction
The Department of Housing and Community Development (HCD) in Emil City seeks to launch a targeted campaign to encourage homeowners to take advantage of a $10,000 tax credit for home repairs. Typically, only 11% of the eligible homeowners they reach out to take the credit. This analysis attempts to improve the efficiency of HCD's outreach efforts, minimizing outreach to homeowners who are unlikely to take the credit while maximizing outreach to homeowners who are likely to take the credit.

### Set Up 
```{r setup, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(error = FALSE)

options(scipen=10000000)

library(tidyverse)
library(kableExtra)
library(caret)
library(knitr) 
library(pscl)
library(plotROC)
library(pROC)
library(lubridate)
library(ggcorrplot)
library(gridExtra)

palette5 <- c("#981FAC","#CB0F8B","#FF006A","#FE4C35","#FE9900")
palette4 <- c("#981FAC","#FF006A","#FE4C35","#FE9900")
palette2 <- c("#981FAC","#FF006A")

house_subsidy <- read.csv("DATA/housingSubsidy.csv")
```

# Data Visualizations
The mean age of those who take the credit is slightly higher than the mean age of eligible homeowners that do not take the credit

The mean number of times homeowners were contacted within one campaign is higher for those who do not take the credit

The mean consumer confidence index and mean consumer price index at the time of the campaign is about the same for those who take the credit and those who do not

NOTE: need to change pdays because 999 represents no previous contact

The mean number of contacts prior to this campaign is higher for those who take the credit than those who do not

The mean amount of money spent annually on repairs is about the same

Unemployment rate????

Not  sure how to interpret the plots that aren't means (categorical variables)


```{r data_vis, warning=FALSE, message=FALSE}
##continuous variables
house_subsidy %>%
  dplyr::select(y,unemploy_rate, spent_on_repairs, age, campaign, 
                previous,cons.price.idx,cons.conf.idx) %>%
  rename("Unemployment Rate" = unemploy_rate, "$ Spent on Repairs" = spent_on_repairs, "Age of Homeowner"=age, "# of contacts"=campaign, "# of previous contacts"=previous, "Cons. Price Index"=cons.price.idx, "Cons. Conf. Index"=cons.conf.idx) %>%
  gather(Variable, value, -y) %>%
  ggplot(aes(y, value, fill=y)) + 
  geom_bar(position = "dodge", stat = "summary", fun = "mean") + 
  facet_wrap(~Variable, scales = "free") +
  scale_fill_manual(values = palette2) +
  labs(x="y", y="Value", 
       title = "Feature associations with the likelihood of taking credit",
       subtitle = "(continous outcomes)") +
  theme(legend.position = "none")
```

Interpretation - these plots are not useful because they aren't normalized and have count associated, not mean
```{r data_vis2, warning=FALSE, message=FALSE, fig.width= 10,fig.height=12}
# NOT WORKING
house_subsidy$month <-ordered(house_subsidy$month, 
                             levels=c("mar","apr","may","jun","jul","aug","sep","oct","nov","dec"))

house_subsidy$day_of_week <-ordered(house_subsidy$day_of_week, 
                             levels=c("mon","tue","wed","thu","fri"))

## categorical variables
grid.arrange(ncol=3,
house_subsidy %>%
  dplyr::select(y, education) %>%
  gather(Variable, value, -y) %>%
  count(Variable, value, y) %>%
  ggplot(aes(value, n, fill = y)) +   
  geom_bar(position = "dodge", stat="identity") +
  facet_wrap(~Variable, scales="free") +
  scale_fill_manual(values = palette2) +
  labs(x="\n Take Credit", y="Count",
       title = "Education association \nwith likelihood of taking credit")+
  theme(axis.text.x = element_text(angle = 45)),
     

## Jobs
house_subsidy %>%
  dplyr::select(y, job) %>%
  gather(Variable, value, -y) %>%
  count(Variable, value, y) %>%
  ggplot(aes(value, n, fill = y)) +   
  geom_bar(position = "dodge", stat="identity") +
  facet_wrap(~Variable, scales="free") +
  scale_fill_manual(values = palette2) +
  labs(x="\n Take Credit", y="Count",
       title = "Job type association \nwith likelihood of taking credit")+
  theme(axis.text.x = element_text(angle = 45)),

## Marital
house_subsidy %>%
  dplyr::select(y, marital) %>%
  gather(Variable, value, -y) %>%
  count(Variable, value, y) %>%
  ggplot(aes(value, n, fill = y)) +   
  geom_bar(position = "dodge", stat="identity") +
  facet_wrap(~Variable, scales="free") +
  scale_fill_manual(values = palette2) +
  labs(x="\n Take Credit", y="Count",
       title = "Marital status association \nwith likelihood of taking credit")+
  theme(axis.text.x = element_text(angle = 45)),

## taxLien
house_subsidy %>%
  dplyr::select(y, taxLien) %>%
  gather(Variable, value, -y) %>%
  count(Variable, value, y) %>%
  ggplot(aes(value, n, fill = y)) +   
  geom_bar(position = "dodge", stat="identity") +
  facet_wrap(~Variable, scales="free") +
  scale_fill_manual(values = palette2) +
  labs(x="\n Take Credit", y="Count",
       title = "Tax Lien association \nwith likelihood of taking credit")+
  theme(axis.text.x = element_text(angle = 45)),

house_subsidy %>%
  dplyr::select(y, mortgage) %>%
  gather(Variable, value, -y) %>%
  count(Variable, value, y) %>%
  ggplot(aes(value, n, fill = y)) +   
  geom_bar(position = "dodge", stat="identity") +
  facet_wrap(~Variable, scales="free") +
  scale_fill_manual(values = palette2) +
  labs(x="\n Take Credit", y="Count",
       title = "Mortgag association \nwith likelihood of taking credit")+
  theme(axis.text.x = element_text(angle = 45)),

house_subsidy %>%
  dplyr::select(y, taxbill_in_phl) %>%
  gather(Variable, value, -y) %>%
  count(Variable, value, y) %>%
  ggplot(aes(value, n, fill = y)) +   
  geom_bar(position = "dodge", stat="identity") +
  facet_wrap(~Variable, scales="free") +
  scale_fill_manual(values = palette2) +
  labs(x="\n Take Credit", y="Count",
       title = "Full-time residence in Philly association \nwith likelihood of taking credit")+
  theme(axis.text.x = element_text(angle = 45)),

house_subsidy %>%
  dplyr::select(y, contact) %>%
  gather(Variable, value, -y) %>%
  count(Variable, value, y) %>%
  ggplot(aes(value, n, fill = y)) +   
  geom_bar(position = "dodge", stat="identity") +
  facet_wrap(~Variable, scales="free") +
  scale_fill_manual(values = palette2) +
  labs(x="\n Take Credit", y="Count",
       title = "Previous contact association \nwith likelihood of taking credit")+
  theme(axis.text.x = element_text(angle = 45)),

# Change order of months
house_subsidy %>%
  dplyr::select(y, month) %>%
  gather(Variable, value, -y) %>%
  count(Variable, value, y) %>%
  ggplot(aes(value, n, fill = y)) +   
  geom_bar(position = "dodge", stat="identity") +
  facet_wrap(~Variable, scales="free") +
  scale_fill_manual(values = palette2) +
  labs(x="\n Take Credit", y="Count",
       title = "Month contacted association \nwith likelihood of taking credit")+
  theme(axis.text.x = element_text(angle = 45)),

# Change order of days
house_subsidy %>%
  dplyr::select(y, day_of_week) %>%
  gather(Variable, value, -y) %>%
  count(Variable, value, y) %>%
  ggplot(aes(value, n, fill = y)) +   
  geom_bar(position = "dodge", stat="identity") +
  facet_wrap(~Variable, scales="free") +
  scale_fill_manual(values = palette2) +
  labs(x="\n Take Credit", y="Count",
       title = "Day contacted association \nwith likelihood of taking credit")+
  theme(axis.text.x = element_text(angle = 45)),

house_subsidy %>%
  dplyr::select(y, poutcome) %>%
  gather(Variable, value, -y) %>%
  count(Variable, value, y) %>%
  ggplot(aes(value, n, fill = y)) +   
  geom_bar(position = "dodge", stat="identity") +
  facet_wrap(~Variable, scales="free") +
  scale_fill_manual(values = palette2) +
  labs(x="\n Take Credit", y="Count",
       title = "Outcome of previous campaign association \nwith likelihood of taking credit")+
  theme(axis.text.x = element_text(angle = 45))
)
```

### Feature Engineering
One paragraph interpreting new features
employment status matters more than type of job
Seasons may impact when people are thinking about house repairs
days of week - beginning/end of week vs. middle of week, when are going to be more receptive to the marketing campaign

Employment status plot weird b/c dummy var
Struggling with interpretation of these - ask Matthew?

```{r data, message=FALSE, warning=FALSE, fig.width= 12,fig.height=8}
## Data wrangling
### Employment 

house_subsidy <-
  house_subsidy %>%
  mutate(Employment = ifelse(house_subsidy$job == "blue-collar"|house_subsidy$job == "services"|house_subsidy$job =="admin."|house_subsidy$job =="entrepreneur"|
                               house_subsidy$job =="self-employed"|house_subsidy$job =="technician"|house_subsidy$job =="management"|
                               house_subsidy$job =="housemaid",1,0))
### Pdays 
house_subsidy <-
  house_subsidy %>%
  mutate(Pdays_group = case_when(
    pdays >= 1 & pdays <= 7 ~ "In a week",
    pdays >= 8 & pdays <= 14  ~ "Second week",
    pdays >= 15 & pdays <= 21  ~ "Third week",
    pdays >= 22 & age < 999  ~ "After a month",
    pdays >= 999   ~ "Never contacted"))

### Age
house_subsidy <-
  house_subsidy %>%
  mutate(Age_group = case_when(
    age < 18 ~ "Less than 18",
    age >= 18 & age < 25  ~ "18-25",
    age >= 25 & age < 35  ~ "25-35",
    age >= 35 & age <= 50  ~ "35-50",
    age >= 50 & age < 65   ~ "50-65",
    age >= 65   ~ "Above 65"))

### Education
house_subsidy <-
  house_subsidy %>%
  mutate(Education_group = case_when(
    education == "basic.9y" |education == "basic.6y" | education == "basic.4y" ~ "Basics",
    education == "high.school"  ~ "High School",
    education == "university.degree" |education == "professional.course"  ~ "College",
    education == "unknown" |education == "illiterate"  ~ "Illiterate"))

### Seasons
house_subsidy <-
  house_subsidy %>%
  mutate(Season = case_when(
    month == "dec" |month == "jan" | month == "feb" ~ "Winter",
    month == "mar" |month == "apr" | month == "may" ~ "Spring",
    month == "jun" |month == "jul" | month == "aug" ~ "Summer",
    month == "sep" |month == "oct" | month == "nov" ~ "Fall"))

### Day
house_subsidy <-
  house_subsidy %>%
  mutate(Day = case_when(
    day_of_week == "mon" |day_of_week == "fri" ~ "Busy",
    day_of_week == "tue" |day_of_week == "wed" | day_of_week == "thu" ~ "Non-busy"))


grid.arrange (ncol=3,
house_subsidy %>%
  dplyr::select(y, Employment) %>%
  gather(Variable, value, -y) %>%
  count(Variable, value, y) %>%
  ggplot(aes(value, n, fill = y)) +   
  geom_bar(position = "dodge", stat="identity") +
  facet_wrap(~Variable, scales="free") +
  scale_fill_manual(values = palette2) +
  labs(x="Take Credit", y="Count",
       title = "Employment status association \nwith likelihood of taking credit"),

house_subsidy %>%
  dplyr::select(y, Age_group) %>%
  gather(Variable, value, -y) %>%
  count(Variable, value, y) %>%
  ggplot(aes(value, n, fill = y)) +   
  geom_bar(position = "dodge", stat="identity") +
  facet_wrap(~Variable, scales="free") +
  scale_fill_manual(values = palette2) +
  labs(x="Take Credit", y="Count",
       title = "Age group association \nwith likelihood of taking credit"),

house_subsidy %>%
  dplyr::select(y, Education_group) %>%
  gather(Variable, value, -y) %>%
  count(Variable, value, y) %>%
  ggplot(aes(value, n, fill = y)) +   
  geom_bar(position = "dodge", stat="identity") +
  facet_wrap(~Variable, scales="free") +
  scale_fill_manual(values = palette2) +
  labs(x="Take Credit", y="Count",
       title = "Education group association \nwith likelihood of taking credit"),

house_subsidy %>%
  dplyr::select(y, Season) %>%
  gather(Variable, value, -y) %>%
  count(Variable, value, y) %>%
  ggplot(aes(value, n, fill = y)) +   
  geom_bar(position = "dodge", stat="identity") +
  facet_wrap(~Variable, scales="free") +
  scale_fill_manual(values = palette2) +
  labs(x="Take Credit", y="Count",
       title = "Season contacted association \nwith likelihood of taking credit"),

house_subsidy %>%
  dplyr::select(y, Day) %>%
  gather(Variable, value, -y) %>%
  count(Variable, value, y) %>%
  ggplot(aes(value, n, fill = y)) +   
  geom_bar(position = "dodge", stat="identity") +
  facet_wrap(~Variable, scales="free") +
  scale_fill_manual(values = palette2) +
  labs(x="Take Credit", y="Count",
       title = "Day contacted association \nwith likelihood of taking credit"),

house_subsidy %>%
  dplyr::select(y, Pdays_group) %>%
  gather(Variable, value, -y) %>%
  count(Variable, value, y) %>%
  ggplot(aes(value, n, fill = y)) +   
  geom_bar(position = "dodge", stat="identity") +
  facet_wrap(~Variable, scales="free") +
  scale_fill_manual(values = palette2) +
  labs(x="Take Credit", y="Count",
       title = "Time associated with contacted association \nwith likelihood of taking credit"))

```

## Correlation
This plot shows that none of our numeric variables are strongly correlated with whether or not an eligible homeowner takes the credit. 

The plot suggests that some of our numeric variables may be colinear. The unemployment rate at time of contact is strongly positively correlated with the inflation rate at time of contact. The inflation rate at time of contact is also strongly positively correlated with the amount of money spent annually on repairs.
```{r correlation, message=FALSE, warning=FALSE}

numericVars1 <- 
  select_if(house_subsidy, is.numeric) %>% na.omit() %>%
  dplyr::select(age, unemploy_rate, cons.price.idx, cons.conf.idx, inflation_rate, spent_on_repairs,y_numeric)

ggcorrplot(
  round(cor(numericVars1), 1), 
  p.mat = cor_pmat(numericVars1),
  colors = c("#25CB10", "white", "#FA7800"),
  type="lower",
  insig = "blank") +  
  labs(title = "Correlation across Characteristics") 


```

# Compare Models

A very predictive regression would show clustering of 0 (don't take the credit) around 0 and clustering of 1 (do take the credit) around 1. Neither model shows clustering around 1, indicating that these models have poor sensitivity.

Need to add something about confusion matrix
true positive means blah blah blah
true negative means blah blah blah
false positive means
false negative

Compare confusion matrices of both regressions
```{r regs, message=FALSE, warning=FALSE}
#house_subsidy <- rename(house_subsidy,y.numeric=y_numeric)

set.seed(3456)
trainIndex <- createDataPartition(house_subsidy$y, p = .65, 
                                  y = paste(house_subsidy$Education_group,house_subsidy$Age_group,house_subsidy$Season,house_subsidy$Employment,house_subsidy$taxLien),
                                  list = FALSE,
                                  times = 1)
housingTrain <- house_subsidy[ trainIndex,]
housingTest  <- house_subsidy[-trainIndex,]

## Regression
### Kichen Sink Model

kitchensink <- glm(y_numeric ~ .,
                    data=housingTrain %>% 
                      dplyr::select(-X, -Season, -Education_group,-Age_group,-Employment, -Day, -y, -Pdays_group),
                    family="binomial" (link="logit"))

summary(kitchensink)
  
housingModel <- glm(y_numeric ~ .,
                    data=housingTrain %>% 
                      dplyr::select(-y,-X, -contact,-month,-day_of_week,-poutcome,-Age_group, 
                                 -education, -job),
                    family="binomial" (link="logit"))

summary(housingModel)

## Adding Coefficients
x <- housingModel$coefficients
exp(x)


## Fit metrics
# pR2(kitchensink)
pR2(housingModel)

## Prediction
testProbs <- data.frame(Outcome = as.factor(housingTest$y_numeric),
                        Probs = predict(housingModel, housingTest, type= "response"))

testProbs$Probs <- ifelse(is.na(testProbs$Probs), 0.1043699, testProbs$Probs) 

testProbskitchensink <- data.frame(Outcome = as.factor(housingTest$y_numeric),
                        Probs = predict(kitchensink, housingTest, type= "response"))

#Here we want more of a hump in the bottom plot around 1 to indicate that the reg is predictive
ggplot(testProbskitchensink, aes(x = Probs, fill = as.factor(Outcome))) + 
  geom_density() +
  facet_grid(Outcome ~ .) +
  scale_fill_manual(values = palette2) +
  labs(x = "Click", y = "Density of probabilities",
       title = "Distribution of predicted probabilities by observed outcome",
       subtitle = "Kitchen Sink Model") +
  theme(strip.text.x = element_text(size = 18),
        legend.position = "none")

ggplot(testProbs, aes(x = Probs, fill = as.factor(Outcome))) + 
  geom_density() +
  facet_grid(Outcome ~ .) +
  scale_fill_manual(values = palette2) +
  labs(x = "Click", y = "Density of probabilities",
       title = "Distribution of predicted probabilities by observed outcome",
       subtitle = "Model with Feature Engineering") +
  theme(strip.text.x = element_text(size = 18),
        legend.position = "none")

## Confusion matrix
### Might want to change this threshold, here a probability >50% if being predicted as takes credit
testProbskitchensink <- 
  testProbskitchensink %>%
  mutate(predOutcome  = as.factor(ifelse(testProbskitchensink$Probs > 0.5 , 1, 0)))

caret::confusionMatrix(testProbskitchensink$predOutcome, testProbskitchensink$Outcome, 
                       positive = "1")

testProbs <- 
  testProbs %>%
  mutate(predOutcome  = as.factor(ifelse(testProbs$Probs >= 0.5 , 1, 0)))

caret::confusionMatrix(testProbs$predOutcome, testProbs$Outcome, 
                       positive = "1")
```

## Cross Validation
Compare and interpret two facetted plots of ROC, sensitivity, and specificity
Ours is (sometimes) worse :(
```{r cv, message=FALSE, warning=FALSE, fig.width= 8, fig.height=4}


## Cross validation
ctrl <- trainControl(method = "cv", number = 100, classProbs=TRUE, summaryFunction=twoClassSummary)

cvFitkitchensink <-train(y ~ .,
               data=house_subsidy %>% 
                 dplyr::select(-X, -y_numeric, -Season, -Education_group,-Age_group,-Employment, -Day, -Pdays_group) %>%
                 dplyr::mutate(y = ifelse(y=="yes","c1.yes","c2.no")),
               method="glm", family="binomial",
               metric="ROC", trControl = ctrl)
  
cvFitkitchensink

cvFit <- train(y ~ .,
                data=house_subsidy %>% 
                  dplyr::select(-y_numeric,-X, -contact,-month,-day_of_week,-poutcome,-Age_group, 
                                 -education, -job, -Pdays_group) %>%
                  dplyr::mutate(y = ifelse(y=="yes","c1.yes","c2.no")), 
                method="glm", family="binomial",
                metric="ROC", trControl = ctrl)


cvFit

## Goodness metrics
grid.arrange(ncol = 2,

  dplyr::select(cvFitkitchensink$resample, -Resample) %>%
  gather(metric, value) %>%
  left_join(gather(cvFitkitchensink$results[2:4], metric, mean)) %>%
  ggplot(aes(value)) + 
  geom_histogram(bins=35, fill = "#FF006A") +
  facet_wrap(~metric) +
  geom_vline(aes(xintercept = mean), colour = "#981FAC", linetype = 3, size = 1.5) +
  scale_x_continuous(limits = c(0, 1)) +
  labs(x="Goodness of Fit", y="Count", title="CV Goodness of Fit Metrics Kitchen Sink Model",
       subtitle = "Across-fold mean reprented as dotted lines"),


  dplyr::select(cvFit$resample, -Resample) %>%
  gather(metric, value) %>%
  left_join(gather(cvFit$results[2:4], metric, mean)) %>%
  ggplot(aes(value)) + 
  geom_histogram(bins=35, fill = "#FF006A") +
  facet_wrap(~metric) +
  geom_vline(aes(xintercept = mean), colour = "#981FAC", linetype = 3, size = 1.5) +
  scale_x_continuous(limits = c(0, 1)) +
  labs(x="Goodness of Fit", y="Count", title="CV Goodness of Fit Metrics \n Feature Engineered Model",
       subtitle = "Across-fold mean reprented as dotted lines"))
```


### Receiver Operating Characteristic Curve
Interpret ROC curve for new model
Visualizes trade-offs of the model.When increase true positives, also increase false positives, that means HCD will waste money on marketing

add explanation about trade offs for thresholds

explain AUC,100% is overfit, 50% would be coin flip, this indicates that our model predicts reasonably well and is generalizable, this is a goodness of fit metric
```{r ROC, warning=FALSE, message=FALSE}
## ROC curve
# This us a goodness of fit measure, 1 would be a perfect fit, .5 is a coin toss
auc(testProbs$Outcome, testProbs$Probs)

ggplot(testProbs, aes(d = as.numeric(testProbs$Outcome), m = Probs)) +
  geom_roc(n.cuts = 50, labels = FALSE, colour = "#FE9900") +
  style_roc(theme = theme_grey) +
  geom_abline(slope = 1, intercept = 0, size = 1.5, color = 'grey') +
  labs(title = "ROC Curve - Model with Feature Engineering")
```

# Cost/Benefit Analysis
Write out the cost/benefit equation for each confusion metric
We chose to split HCD expenditures and value addd to houses
Explain why false negatives are 0
Explain why did not multiply by 25%, it is stupid and makes no sense, our analysts are smarter
Use confusion matrix numbers to show why the 25% math doesn't work

```{r cb_analysis, message=FALSE, warning=FALSE}
## Cost benefit
cost_benefit_table <-
  testProbs %>%
  count(predOutcome, Outcome) %>%
  summarize(True_Negative = sum(n[predOutcome==0 & Outcome==0]),
                True_Positive = sum(n[predOutcome==1 & Outcome==1]),
                False_Negative = sum(n[predOutcome==0 & Outcome==1]),
                False_Positive = sum(n[predOutcome==1 & Outcome==0])) %>%
  gather(Variable, Count) %>%
  mutate(HCD_Expenditure =
           case_when(Variable == "True_Negative" ~ Count*0,
                Variable == "True_Positive" ~ (Count*2850)+(Count*5000*.25),
                Variable == "False_Negative" ~ Count*0,
                Variable == "False_Positive" ~ (Count*2850))) %>%
  mutate(Home_Value_Added =
           case_when(Variable == "True_Negative" ~ Count*0,
                Variable == "True_Positive" ~ (Count*10000)+(Count*56000),
                Variable == "False_Negative" ~ Count*0,
                Variable == "False_Positive" ~ -(Count*0))) %>%
  mutate(Number_Credits =
           case_when(Variable == "True_Negative" ~ Count*0,
                     Variable == "True_Positive" ~ Count*1,
                     Variable == "False_Negative" ~ Count*0,
                     Variable == "False_Positive" ~ Count*0)) %>%
  bind_cols(data.frame(Description = c(
    "We correctly predicted not taking credit",
    "We correctly predicted taking credit",
    "We predicted would not take credit and customer took credit",
    "We predicted customer would take credit and customer did not take credit")))

kable(cost_benefit_table,
      caption = "Cost/Benefit Table") %>% kable_styling()
```

## Comparing Thresholds
Plot confusion metrics for each threshold
create two small multiple plots to show Threshold as a function of Total_Revenue and Total_Count_of_Credits; interpret
Create a table ofTotal_Revenue and Total_Count_of_Credits for 2 categories, 50% and optimal threshold -- NEED TO ADD THIS

explain that can't see true neg because rev also 0
Explain why put together HCD expenditures and added household here, because goal is to minimize expenditures and maximize hosuehold values
Also separate them into HCD spending an house value

```{r thresholds, message=FALSE, warning=FALSE}
## Optimise threshold
iterateThresholds <- function(data) {
  x = .01
  all_prediction <- data.frame()
  while (x <= 1) {
    
    this_prediction <-
      testProbs %>%
      mutate(predOutcome = ifelse(Probs > x, 1, 0)) %>%
      count(predOutcome, Outcome) %>%
      summarize(True_Negative = sum(n[predOutcome==0 & Outcome==0]),
                True_Positive = sum(n[predOutcome==1 & Outcome==1]),
                False_Negative = sum(n[predOutcome==0 & Outcome==1]),
                False_Positive = sum(n[predOutcome==1 & Outcome==0])) %>%
      gather(Variable, Count) %>%
      mutate(HCD_Expenditure =
             case_when(Variable == "True_Negative" ~ Count*0,
                Variable == "True_Positive" ~ (Count*2850)+(Count*5000*.25),
                Variable == "False_Negative" ~ Count*0,
                Variable == "False_Positive" ~ (Count*2850)), 
            Threshold = x,
            Number_Credits =
               ifelse(Variable == "True_Negative", Count * 0,
               ifelse(Variable == "True_Positive", (Count*1),
               ifelse(Variable == "False_Negative", Count*0,
               ifelse(Variable == "False_Positive", Count*0,0)))),
            Home_Value_Added =
           case_when(Variable == "True_Negative" ~ Count*0,
                Variable == "True_Positive" ~ (Count*10000)+(Count*56000),
                Variable == "False_Negative" ~ Count*0,
                Variable == "False_Positive" ~ -(Count*0)),
           Revenue =
           case_when(Variable == "True_Negative" ~ Count*0,
                Variable == "True_Positive" ~ ((Count*.25*10000) + (Count*.25*56000)-(Count*2850)-(Count*.25*5000)),
                Variable == "False_Negative" ~ Count*0,
                Variable == "False_Positive" ~ -(Count*2850)))
    
    all_prediction <- rbind(all_prediction, this_prediction)
    x <- x + .01
  }
  return(all_prediction)
}

whichThreshold <- iterateThresholds(testProbs)

whichThreshold_revenue <- 
  whichThreshold %>% 
  group_by(Threshold) %>% na.omit() %>%
  summarize(Revenue = sum(Revenue))

ggplot(whichThreshold_revenue)+
  geom_line(aes(x = Threshold, y = Revenue))+
  geom_vline(xintercept =  pull(arrange(whichThreshold_revenue, -Revenue)[1,1]))+
  labs(title = "Model Revenues By Threshold For Test Sample",
       subtitle = "Vertical Line Denotes Optimal Threshold")

whichThreshold_hcd <- 
  whichThreshold %>% 
  group_by(Threshold) %>% na.omit() %>%
  summarize(HCD_Expenditure = sum(HCD_Expenditure),
            Home_Value_Added = sum(Home_Value_Added))

ggplot(whichThreshold_hcd)+
  geom_line(aes(x = Threshold, y = HCD_Expenditure, color = "HCD_Expenditure"))+
  geom_line(aes(x = Threshold, y = Home_Value_Added, color = "Home_Value_Added"))+
  labs(title = "Model HCD expense and Home value addition By Threshold For Test Sample")

whichThreshold_credits <- 
  whichThreshold %>% 
  group_by(Threshold) %>% 
  summarize(Number_Credits= sum(Number_Credits))

ggplot(whichThreshold_credits)+
  geom_line(aes(x = Threshold, y = Number_Credits))+
  labs(title = "Model Number of Credits By Threshold For Test Sample")

## Plot confusion metrics for each threshold

whichThreshold %>%
  ggplot(.,aes(Threshold, HCD_Expenditure, colour = Variable)) +
  geom_point() +
  scale_colour_manual(values = palette5[c(5, 1:3)]) +    
  labs(title = "Revenue by confusion metric type and threshold",
       y = "Revenue") +
  #plotTheme() +
  guides(colour=guide_legend(title = "Confusion Metrics")) 

# Optimal Threshold
optimum_threshold <- pull(arrange(whichThreshold_revenue, -Revenue)[1,1])

opt <- 
  whichThreshold %>% 
  group_by(Threshold) %>% 
  summarize(HCD_Expenditure = sum(HCD_Expenditure),
            Home_Value_Added = sum(Home_Value_Added),
            Number_Credits= sum(Number_Credits)) %>%
  filter(Threshold == optimum_threshold)

fifty_thresh <-
  whichThreshold %>% 
  group_by(Threshold) %>% 
  summarize(HCD_Expenditure = sum(HCD_Expenditure),
            Home_Value_Added = sum(Home_Value_Added),
            Number_Credits= sum(Number_Credits)) %>%
  filter(Threshold > .499 & Threshold < .51)

final <- data.frame(rbind(opt, fifty_thresh))

kable(final,
      caption = "Optimum Threshold and 50% Threshold") %>% kable_styling()

```

# Conclusion
Should this model be put into production? What could make the model better? What would you do to ensure that the marketing materials result in a better response rate?