---
title: "MUSA 508 Assignment 4"
author: "Leah Shapiro and Palak Agarwal"
date: "10/28/2020"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
 
---
# Introduction
The Department of Housing and Community Development (HCD) in Emil City seeks to launch a targeted campaign to encourage homeowners to take advantage of a $10,000 tax credit for home repairs. Typically, only 11% of the eligible homeowners they reach out to take the credit. This analysis attempts to improve the efficiency of HCD's outreach efforts, minimizing outreach to homeowners who are unlikely to take the credit while maximizing outreach to homeowners who are likely to take the credit.

### Set Up 
```{r setup, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(error = FALSE)

options(scipen=10000000)

library(tidyverse)
library(kableExtra)
library(caret)
library(knitr) 
library(pscl)
library(plotROC)
library(pROC)
library(lubridate)
library(ggcorrplot)
library(gridExtra)

palette5 <- c("#981FAC","#CB0F8B","#FF006A","#FE4C35","#FE9900")
palette4 <- c("#981FAC","#FF006A","#FE4C35","#FE9900")
palette2 <- c("#981FAC","#FF006A")

house_subsidy <- read.csv("DATA/housingSubsidy.csv")
```

# Data Visualizations
## Continuous Variables
- the mean number of contacts within this camapgin is higher for those who do not take the credit
- the mean number of contacts in previous campaigns is slightly higher for people who do take the credit
-The mean amount of money spent annually on repairs is about the same
-The mean age of those who take the credit is slightly higher than the mean age of eligible homeowners that do not take the credit
-The mean number of times homeowners were contacted within one campaign is higher for those who do not take the credit
-The mean consumer confidence index and mean consumer price index at the time of the campaign is about the same for those who take the credit and those who do not
- Not sure how to interpret unemployment rate, since it ranges from -3.4 to 1.4. The mean unemployment rate is higher, or less negative, for people who do not take the credit

```{r data_vis, warning=FALSE, message=FALSE}
##continuous variables
house_subsidy %>%
  dplyr::select(y,unemploy_rate, spent_on_repairs, age, campaign, 
                previous,cons.price.idx,cons.conf.idx) %>%
  rename("Unemployment Rate" = unemploy_rate, "$ Spent on Repairs" = spent_on_repairs, "Age of Homeowner"=age, "# of contacts"=campaign, "# of previous contacts"=previous, "Cons. Price Index"=cons.price.idx, "Cons. Conf. Index"=cons.conf.idx) %>%
  gather(Variable, value, -y) %>%
  ggplot(aes(y, value, fill=y)) + 
  geom_bar(position = "dodge", stat = "summary", fun = "mean") + 
  facet_wrap(~Variable, scales = "free") +
  scale_fill_manual(values = palette2) +
  labs(x="y", y="Value", 
       title = "Feature associations with the likelihood of taking credit",
       subtitle = "(continous outcomes)") +
  theme(legend.position = "none")
```

## Categorical Variables
Counts of different levels of each categorical variable shown below. These plots are not useful because the data aren't normalized and have count associated with them, not mean
```{r data_vis2, warning=FALSE, message=FALSE, fig.width= 10,fig.height=12}
# NOT WORKING
house_subsidy$month <-ordered(house_subsidy$month, 
                             levels=c("mar","apr","may","jun","jul","aug","sep","oct","nov","dec"))

house_subsidy$day_of_week <-ordered(house_subsidy$day_of_week, 
                             levels=c("mon","tue","wed","thu","fri"))

## categorical variables
grid.arrange(ncol=3,
house_subsidy %>%
  dplyr::select(y, education) %>%
  gather(Variable, value, -y) %>%
  count(Variable, value, y) %>%
  ggplot(aes(value, n, fill = y)) +   
  geom_bar(position = "dodge", stat="identity") +
  facet_wrap(~Variable, scales="free") +
  scale_fill_manual(values = palette2) +
  labs(x="\n Take Credit", y="Count",
       title = "Education association \nwith likelihood of taking credit")+
  theme(axis.text.x = element_text(angle = 45)),
     

## Jobs
house_subsidy %>%
  dplyr::select(y, job) %>%
  gather(Variable, value, -y) %>%
  count(Variable, value, y) %>%
  ggplot(aes(value, n, fill = y)) +   
  geom_bar(position = "dodge", stat="identity") +
  facet_wrap(~Variable, scales="free") +
  scale_fill_manual(values = palette2) +
  labs(x="\n Take Credit", y="Count",
       title = "Job type association \nwith likelihood of taking credit")+
  theme(axis.text.x = element_text(angle = 45)),

## Marital
house_subsidy %>%
  dplyr::select(y, marital) %>%
  gather(Variable, value, -y) %>%
  count(Variable, value, y) %>%
  ggplot(aes(value, n, fill = y)) +   
  geom_bar(position = "dodge", stat="identity") +
  facet_wrap(~Variable, scales="free") +
  scale_fill_manual(values = palette2) +
  labs(x="\n Take Credit", y="Count",
       title = "Marital status association \nwith likelihood of taking credit")+
  theme(axis.text.x = element_text(angle = 45)),

## taxLien
house_subsidy %>%
  dplyr::select(y, taxLien) %>%
  gather(Variable, value, -y) %>%
  count(Variable, value, y) %>%
  ggplot(aes(value, n, fill = y)) +   
  geom_bar(position = "dodge", stat="identity") +
  facet_wrap(~Variable, scales="free") +
  scale_fill_manual(values = palette2) +
  labs(x="\n Take Credit", y="Count",
       title = "Tax Lien association \nwith likelihood of taking credit")+
  theme(axis.text.x = element_text(angle = 45)),

house_subsidy %>%
  dplyr::select(y, mortgage) %>%
  gather(Variable, value, -y) %>%
  count(Variable, value, y) %>%
  ggplot(aes(value, n, fill = y)) +   
  geom_bar(position = "dodge", stat="identity") +
  facet_wrap(~Variable, scales="free") +
  scale_fill_manual(values = palette2) +
  labs(x="\n Take Credit", y="Count",
       title = "Mortgag association \nwith likelihood of taking credit")+
  theme(axis.text.x = element_text(angle = 45)),

house_subsidy %>%
  dplyr::select(y, taxbill_in_phl) %>%
  gather(Variable, value, -y) %>%
  count(Variable, value, y) %>%
  ggplot(aes(value, n, fill = y)) +   
  geom_bar(position = "dodge", stat="identity") +
  facet_wrap(~Variable, scales="free") +
  scale_fill_manual(values = palette2) +
  labs(x="\n Take Credit", y="Count",
       title = "Full-time residence in Philly association \nwith likelihood of taking credit")+
  theme(axis.text.x = element_text(angle = 45)),

house_subsidy %>%
  dplyr::select(y, contact) %>%
  gather(Variable, value, -y) %>%
  count(Variable, value, y) %>%
  ggplot(aes(value, n, fill = y)) +   
  geom_bar(position = "dodge", stat="identity") +
  facet_wrap(~Variable, scales="free") +
  scale_fill_manual(values = palette2) +
  labs(x="\n Take Credit", y="Count",
       title = "Previous contact association \nwith likelihood of taking credit")+
  theme(axis.text.x = element_text(angle = 45)),

# Change order of months
house_subsidy %>%
  dplyr::select(y, month) %>%
  gather(Variable, value, -y) %>%
  count(Variable, value, y) %>%
  ggplot(aes(value, n, fill = y)) +   
  geom_bar(position = "dodge", stat="identity") +
  facet_wrap(~Variable, scales="free") +
  scale_fill_manual(values = palette2) +
  labs(x="\n Take Credit", y="Count",
       title = "Month contacted association \nwith likelihood of taking credit")+
  theme(axis.text.x = element_text(angle = 45)),

# Change order of days
house_subsidy %>%
  dplyr::select(y, day_of_week) %>%
  gather(Variable, value, -y) %>%
  count(Variable, value, y) %>%
  ggplot(aes(value, n, fill = y)) +   
  geom_bar(position = "dodge", stat="identity") +
  facet_wrap(~Variable, scales="free") +
  scale_fill_manual(values = palette2) +
  labs(x="\n Take Credit", y="Count",
       title = "Day contacted association \nwith likelihood of taking credit")+
  theme(axis.text.x = element_text(angle = 45)),

house_subsidy %>%
  dplyr::select(y, poutcome) %>%
  gather(Variable, value, -y) %>%
  count(Variable, value, y) %>%
  ggplot(aes(value, n, fill = y)) +   
  geom_bar(position = "dodge", stat="identity") +
  facet_wrap(~Variable, scales="free") +
  scale_fill_manual(values = palette2) +
  labs(x="\n Take Credit", y="Count",
       title = "Outcome of previous campaign association \nwith likelihood of taking credit")+
  theme(axis.text.x = element_text(angle = 45))
)
```

## Feature Engineering
-employment status matters more than type of job
-number of weeks since last contacted or never contacted
- age range likely to correlate with life stage, who has kids, who is in starter home vs. forever home, etc.
-Seasons may impact when people are thinking about house repairs
days of week - beginning/end of week vs. middle of week, when are going to be more receptive to the marketing campaign
-again these plot aren't useful because data is not normalized
```{r data, message=FALSE, warning=FALSE, fig.width= 12,fig.height=8}
## Data wrangling
### Employment 

house_subsidy <-
  house_subsidy %>%
  mutate(Employment = ifelse(house_subsidy$job == "blue-collar"|house_subsidy$job == "services"|house_subsidy$job =="admin."|house_subsidy$job =="entrepreneur"|
                               house_subsidy$job =="self-employed"|house_subsidy$job =="technician"|house_subsidy$job =="management"|
                               house_subsidy$job =="housemaid",1,0))
### Pdays 
house_subsidy <-
  house_subsidy %>%
  mutate(Pdays_group = case_when(
    pdays >= 1 & pdays <= 7 ~ "In a week",
    pdays >= 8 & pdays <= 14  ~ "Second week",
    pdays >= 15 & pdays <= 21  ~ "Third week",
    pdays >= 22 & age < 999  ~ "After a month",
    pdays >= 999   ~ "Never contacted"))

### Age
house_subsidy <-
  house_subsidy %>%
  mutate(Age_group = case_when(
    age < 18 ~ "Less than 18",
    age >= 18 & age < 25  ~ "18-25",
    age >= 25 & age < 35  ~ "25-35",
    age >= 35 & age <= 50  ~ "35-50",
    age >= 50 & age < 65   ~ "50-65",
    age >= 65   ~ "Above 65"))

### Education
house_subsidy <-
  house_subsidy %>%
  mutate(Education_group = case_when(
    education == "basic.9y" |education == "basic.6y" | education == "basic.4y" ~ "Basics",
    education == "high.school"  ~ "High School",
    education == "university.degree" |education == "professional.course"  ~ "College",
    education == "unknown" |education == "illiterate"  ~ "Illiterate"))

### Seasons
house_subsidy <-
  house_subsidy %>%
  mutate(Season = case_when(
    month == "dec" |month == "jan" | month == "feb" ~ "Winter",
    month == "mar" |month == "apr" | month == "may" ~ "Spring",
    month == "jun" |month == "jul" | month == "aug" ~ "Summer",
    month == "sep" |month == "oct" | month == "nov" ~ "Fall"))

### Day
house_subsidy <-
  house_subsidy %>%
  mutate(Day = case_when(
    day_of_week == "mon" |day_of_week == "fri" ~ "Busy",
    day_of_week == "tue" |day_of_week == "wed" | day_of_week == "thu" ~ "Non-busy"))


grid.arrange (ncol=3,
house_subsidy %>%
  dplyr::select(y, Employment) %>%
  gather(Variable, value, -y) %>%
  count(Variable, value, y) %>%
  ggplot(aes(value, n, fill = y)) +   
  geom_bar(position = "dodge", stat="identity") +
  facet_wrap(~Variable, scales="free") +
  scale_fill_manual(values = palette2) +
  labs(x="Take Credit", y="Count",
       title = "Employment status association \nwith likelihood of taking credit"),

house_subsidy %>%
  dplyr::select(y, Age_group) %>%
  gather(Variable, value, -y) %>%
  count(Variable, value, y) %>%
  ggplot(aes(value, n, fill = y)) +   
  geom_bar(position = "dodge", stat="identity") +
  facet_wrap(~Variable, scales="free") +
  scale_fill_manual(values = palette2) +
  labs(x="Take Credit", y="Count",
       title = "Age group association \nwith likelihood of taking credit"),

house_subsidy %>%
  dplyr::select(y, Education_group) %>%
  gather(Variable, value, -y) %>%
  count(Variable, value, y) %>%
  ggplot(aes(value, n, fill = y)) +   
  geom_bar(position = "dodge", stat="identity") +
  facet_wrap(~Variable, scales="free") +
  scale_fill_manual(values = palette2) +
  labs(x="Take Credit", y="Count",
       title = "Education group association \nwith likelihood of taking credit"),

house_subsidy %>%
  dplyr::select(y, Season) %>%
  gather(Variable, value, -y) %>%
  count(Variable, value, y) %>%
  ggplot(aes(value, n, fill = y)) +   
  geom_bar(position = "dodge", stat="identity") +
  facet_wrap(~Variable, scales="free") +
  scale_fill_manual(values = palette2) +
  labs(x="Take Credit", y="Count",
       title = "Season contacted association \nwith likelihood of taking credit"),

house_subsidy %>%
  dplyr::select(y, Day) %>%
  gather(Variable, value, -y) %>%
  count(Variable, value, y) %>%
  ggplot(aes(value, n, fill = y)) +   
  geom_bar(position = "dodge", stat="identity") +
  facet_wrap(~Variable, scales="free") +
  scale_fill_manual(values = palette2) +
  labs(x="Take Credit", y="Count",
       title = "Day contacted association \nwith likelihood of taking credit"),

house_subsidy %>%
  dplyr::select(y, Pdays_group) %>%
  gather(Variable, value, -y) %>%
  count(Variable, value, y) %>%
  ggplot(aes(value, n, fill = y)) +   
  geom_bar(position = "dodge", stat="identity") +
  facet_wrap(~Variable, scales="free") +
  scale_fill_manual(values = palette2) +
  labs(x="Take Credit", y="Count",
       title = "Time associated with contacted association \nwith likelihood of taking credit"))

```

## Correlations
This plot shows that none of our numeric variables are strongly correlated with whether or not an eligible homeowner takes the credit. 

The plot suggests that some of our numeric variables may be colinear. The unemployment rate at time of contact is strongly positively correlated with the inflation rate at time of contact. The inflation rate at time of contact is also strongly positively correlated with the amount of money spent annually on repairs.
```{r correlation, message=FALSE, warning=FALSE}

numericVars1 <- 
  select_if(house_subsidy, is.numeric) %>% na.omit() %>%
  dplyr::select(age, unemploy_rate, cons.price.idx, cons.conf.idx, inflation_rate, spent_on_repairs,y_numeric)

ggcorrplot(
  round(cor(numericVars1), 1), 
  p.mat = cor_pmat(numericVars1),
  colors = c("#25CB10", "white", "#FA7800"),
  type="lower",
  insig = "blank") +  
  labs(title = "Correlation across Characteristics") 


```

# Compare Models
A very predictive regression would show clustering of 0 (don't take the credit) around 0 and clustering of 1 (do take the credit) around 1. Neither model shows clustering around 1, indicating that these models have poor sensitivity.

Need to add something about confusion matrix
true positive means we predicted they would take the credit and they took it. However, our research suggests that only 25% of our true positives will actually take the credit
true negative means we predicted they would not take the credit and they didn't
false positive means we predicted they would take the credit, but they did not
false negative means we predicted they would not take the credit, but they did

Compare confusion matrices of both regressions
-our model with feature engineering is not better than the "kitchen sink" model. Both have low sensitivities (true positive rate)
```{r regs, message=FALSE, warning=FALSE}
#house_subsidy <- rename(house_subsidy,y.numeric=y_numeric)

set.seed(3456)
trainIndex <- createDataPartition(house_subsidy$y, p = .65, 
                                  y = paste(house_subsidy$Education_group,house_subsidy$Age_group,house_subsidy$Season,house_subsidy$Employment,house_subsidy$taxLien),
                                  list = FALSE,
                                  times = 1)
housingTrain <- house_subsidy[ trainIndex,]
housingTest  <- house_subsidy[-trainIndex,]

## Regression
### Kichen Sink Model

kitchensink <- glm(y_numeric ~ .,
                    data=housingTrain %>% 
                      dplyr::select(-X, -Season, -Education_group,-Age_group,-Employment, -Day, -y, -Pdays_group),
                    family="binomial" (link="logit"))

summary(kitchensink)
  
housingModel <- glm(y_numeric ~ .,
                    data=housingTrain %>% 
                      dplyr::select(-y,-X, -contact,-month,-day_of_week,-poutcome,-Age_group, 
                                 -education, -job),
                    family="binomial" (link="logit"))

summary(housingModel)

## Adding Coefficients
x <- housingModel$coefficients
exp(x)


## Fit metrics
# pR2(kitchensink)
pR2(housingModel)

## Prediction
testProbs <- data.frame(Outcome = as.factor(housingTest$y_numeric),
                        Probs = predict(housingModel, housingTest, type= "response"))

testProbs$Probs <- ifelse(is.na(testProbs$Probs), 0.1043699, testProbs$Probs) 

testProbskitchensink <- data.frame(Outcome = as.factor(housingTest$y_numeric),
                        Probs = predict(kitchensink, housingTest, type= "response"))

#Here we want more of a hump in the bottom plot around 1 to indicate that the reg is predictive
ggplot(testProbskitchensink, aes(x = Probs, fill = as.factor(Outcome))) + 
  geom_density() +
  facet_grid(Outcome ~ .) +
  scale_fill_manual(values = palette2) +
  labs(x = "Click", y = "Density of probabilities",
       title = "Distribution of predicted probabilities by observed outcome",
       subtitle = "Kitchen Sink Model") +
  theme(strip.text.x = element_text(size = 18),
        legend.position = "none")

ggplot(testProbs, aes(x = Probs, fill = as.factor(Outcome))) + 
  geom_density() +
  facet_grid(Outcome ~ .) +
  scale_fill_manual(values = palette2) +
  labs(x = "Click", y = "Density of probabilities",
       title = "Distribution of predicted probabilities by observed outcome",
       subtitle = "Model with Feature Engineering") +
  theme(strip.text.x = element_text(size = 18),
        legend.position = "none")

## Confusion matrix
### Might want to change this threshold, here a probability >50% if being predicted as takes credit
testProbskitchensink <- 
  testProbskitchensink %>%
  mutate(predOutcome  = as.factor(ifelse(testProbskitchensink$Probs > 0.5 , 1, 0)))

caret::confusionMatrix(testProbskitchensink$predOutcome, testProbskitchensink$Outcome, 
                       positive = "1")

testProbs <- 
  testProbs %>%
  mutate(predOutcome  = as.factor(ifelse(testProbs$Probs >= 0.5 , 1, 0)))

caret::confusionMatrix(testProbs$predOutcome, testProbs$Outcome, 
                       positive = "1")
```

## Cross Validation
-test both models using cross-validation. again, shows low sensitivity and high specificity (true negative) rates for both models
-plots show the area under the ROC curve, sensitivity, and specificity. If model were generalizable, would expect all of these plots to be clustered around mean.
```{r cv, message=FALSE, warning=FALSE, fig.width= 8, fig.height=4}


## Cross validation
ctrl <- trainControl(method = "cv", number = 100, classProbs=TRUE, summaryFunction=twoClassSummary)

cvFitkitchensink <-train(y ~ .,
               data=house_subsidy %>% 
                 dplyr::select(-X, -y_numeric, -Season, -Education_group,-Age_group,-Employment, -Day, -Pdays_group) %>%
                 dplyr::mutate(y = ifelse(y=="yes","c1.yes","c2.no")),
               method="glm", family="binomial",
               metric="ROC", trControl = ctrl)
  
cvFitkitchensink

cvFit <- train(y ~ .,
                data=house_subsidy %>% 
                  dplyr::select(-y_numeric,-X, -contact,-month,-day_of_week,-poutcome,-Age_group, 
                                 -education, -job, -Pdays_group) %>%
                  dplyr::mutate(y = ifelse(y=="yes","c1.yes","c2.no")), 
                method="glm", family="binomial",
                metric="ROC", trControl = ctrl)


cvFit

## Goodness metrics
grid.arrange(ncol = 2,

  dplyr::select(cvFitkitchensink$resample, -Resample) %>%
  gather(metric, value) %>%
  left_join(gather(cvFitkitchensink$results[2:4], metric, mean)) %>%
  ggplot(aes(value)) + 
  geom_histogram(bins=35, fill = "#FF006A") +
  facet_wrap(~metric) +
  geom_vline(aes(xintercept = mean), colour = "#981FAC", linetype = 3, size = 1.5) +
  scale_x_continuous(limits = c(0, 1)) +
  labs(x="Goodness of Fit", y="Count", title="CV Goodness of Fit Metrics Kitchen Sink Model",
       subtitle = "Across-fold mean reprented as dotted lines"),


  dplyr::select(cvFit$resample, -Resample) %>%
  gather(metric, value) %>%
  left_join(gather(cvFit$results[2:4], metric, mean)) %>%
  ggplot(aes(value)) + 
  geom_histogram(bins=35, fill = "#FF006A") +
  facet_wrap(~metric) +
  geom_vline(aes(xintercept = mean), colour = "#981FAC", linetype = 3, size = 1.5) +
  scale_x_continuous(limits = c(0, 1)) +
  labs(x="Goodness of Fit", y="Count", title="CV Goodness of Fit Metrics \n Feature Engineered Model",
       subtitle = "Across-fold mean reprented as dotted lines"))
```


## Receiver Operating Characteristic Curve
-Visualizes trade-offs of the model.When increase true positives, also increase false positives, that means HCD will waste money on marketing
-explain AUC,100% is overfit, 50% would be coin flip, this indicates that our model predicts reasonably well and is generalizable, this is a goodness of fit metric
```{r ROC, warning=FALSE, message=FALSE}
## ROC curve
# This us a goodness of fit measure, 1 would be a perfect fit, .5 is a coin toss
auc(testProbs$Outcome, testProbs$Probs)

ggplot(testProbs, aes(d = as.numeric(testProbs$Outcome), m = Probs)) +
  geom_roc(n.cuts = 50, labels = FALSE, colour = "#FE9900") +
  style_roc(theme = theme_grey) +
  geom_abline(slope = 1, intercept = 0, size = 1.5, color = 'grey') +
  labs(title = "ROC Curve - Model with Feature Engineering")
```

# Cost/Benefit Analysis
Split this into HCD expenditures and increases to house values:

-True negative: no HCD expenditure, no housing increases, Count*0

- True positive: HCD spends $2850 on marketing for all true positives and $5000 on tax credit for the 25% that actually take it, equation is (Count*2850)+(Count*.25*5000); benefit is $10000 increase in home value plus $56000 increase in value of surrounding homes, equation is (.25*Count*10000)+(.25*Count*56000)

- false negative: HCD did not spend money on marketing, but homeowner still took credit. Since we are analyzing impact of marketing campaign, we zero this out. Equation for both is Count*0

- false positive: HCD spends money on marketing, equation is count*2850. No increase in values to homes. Equation is Count*0

```{r cb_analysis, message=FALSE, warning=FALSE}
## Cost benefit
cost_benefit_table <-
  testProbs %>%
  count(predOutcome, Outcome) %>%
  summarize(True_Negative = sum(n[predOutcome==0 & Outcome==0]),
                True_Positive = sum(n[predOutcome==1 & Outcome==1]),
                False_Negative = sum(n[predOutcome==0 & Outcome==1]),
                False_Positive = sum(n[predOutcome==1 & Outcome==0])) %>%
  gather(Variable, Count) %>%
  mutate(HCD_Expenditure =
           case_when(Variable == "True_Negative" ~ Count*0,
                Variable == "True_Positive" ~ (Count*2850)+(Count*5000*.25),
                Variable == "False_Negative" ~ Count*0,
                Variable == "False_Positive" ~ (Count*2850))) %>%
  mutate(Home_Value_Added =
           case_when(Variable == "True_Negative" ~ Count*0,
                Variable == "True_Positive" ~ (Count*.25*10000)+(Count*.25*56000),
                Variable == "False_Negative" ~ Count*0,
                Variable == "False_Positive" ~ -(Count*0))) %>%
  mutate(Number_Credits =
           case_when(Variable == "True_Negative" ~ Count*0,
                     Variable == "True_Positive" ~ Count*.25,
                     Variable == "False_Negative" ~ Count*0,
                     Variable == "False_Positive" ~ Count*0)) %>%
  bind_cols(data.frame(Description = c(
    "We correctly predicted not taking credit",
    "We correctly predicted taking credit",
    "We predicted would not take credit and customer took credit",
    "We predicted customer would take credit and customer did not take credit")))

kable(cost_benefit_table,
      caption = "Cost/Benefit Table") %>% kable_styling()
```

## Comparing Thresholds
### Confusion Metric Plots
- for HCD expenditure by confusion metric, explain that can't see true negative because it is also 0
-this plot shows that the HCD expenditure on false positives decreases steeply as threshold increases until a threshold of about 12.5
- for added value to homes by confusion metric plot, value added would be highest at a threshold of 0. However, a lot of money would be wasted on marketing, as seen in the previous plot

```{r confmetrics, message=FALSE, warning=FALSE}

## Optimise threshold
iterateThresholds <- function(data) {
  x = .01
  all_prediction <- data.frame()
  while (x <= 1) {
    
    this_prediction <-
      testProbs %>%
      mutate(predOutcome = ifelse(Probs > x, 1, 0)) %>%
      count(predOutcome, Outcome) %>%
      summarize(True_Negative = sum(n[predOutcome==0 & Outcome==0]),
                True_Positive = sum(n[predOutcome==1 & Outcome==1]),
                False_Negative = sum(n[predOutcome==0 & Outcome==1]),
                False_Positive = sum(n[predOutcome==1 & Outcome==0])) %>%
      gather(Variable, Count) %>%
      mutate(HCD_Expenditure =
             case_when(Variable == "True_Negative" ~ Count*0,
                Variable == "True_Positive" ~ (Count*2850)+(Count*5000*.25),
                Variable == "False_Negative" ~ Count*0,
                Variable == "False_Positive" ~ (Count*2850)), 
            Threshold = x,
            Number_Credits =
               ifelse(Variable == "True_Negative", Count * 0,
               ifelse(Variable == "True_Positive", (Count*.25),
               ifelse(Variable == "False_Negative", Count*0,
               ifelse(Variable == "False_Positive", Count*0,0)))),
            Home_Value_Added =
           case_when(Variable == "True_Negative" ~ Count*0,
                Variable == "True_Positive" ~ (Count*10000*.25)+(Count*56000*.25),
                Variable == "False_Negative" ~ Count*0,
                Variable == "False_Positive" ~ -(Count*0)),
           Revenue =
           case_when(Variable == "True_Negative" ~ Count*0,
                Variable == "True_Positive" ~ ((Count*.25*10000) + (Count*.25*56000)-(Count*2850)-(Count*.25*5000)),
                Variable == "False_Negative" ~ Count*0,
                Variable == "False_Positive" ~ -(Count*2850)))
    
    all_prediction <- rbind(all_prediction, this_prediction)
    x <- x + .01
  }
  return(all_prediction)
}

whichThreshold <- iterateThresholds(testProbs)


## Plot confusion metrics for each threshold
whichThreshold %>%
  ggplot(.,aes(Threshold, HCD_Expenditure, colour = Variable)) +
  geom_point() +
  scale_colour_manual(values = palette5[c(5, 1:3)]) +    
  labs(title = "HCD Expenditure by confusion metric type and threshold",
       y = "Expenditure") +
  #plotTheme() +
  guides(colour=guide_legend(title = "Confusion Metrics")) 

whichThreshold %>% filter(Variable == "True_Positive") %>%
  ggplot(.,aes(Threshold, Home_Value_Added, colour = Variable)) +
  geom_point() +
  scale_colour_manual(values = "#FF006A") +    
  labs(title = "Value added to homes by true positive metric and threshold",
       y = "Value added") +
  #plotTheme() +
  guides(colour=guide_legend(title = "Confusion Metric")) 
```


### Threshold Plots
- First plot shows both HCD expenditures and value added to homes for each threshold. The goal is to minimize HCD expenditures while maximizing value added to homes
-The second plot combines these terms, taking the value added to homes and subtracting HCD expenditures for each threshold. This shows that the optimal threshold is about .2, meaning any homeowner with a 20% probability of taking the credit is considered a "positive" case. This plot also shows that at thresholds below about 10%, HCD spends more money than is gained by adding value to houses
- the third plot shows the number of tax credits claimed at each threshold.This shows that the highest number of tax credits would be claimed with a very low threshold, meaning almost every eligible homeowner would receive marketing materials. However, the previous plots show that this would cost too much money compared to the financial benefits to the homeowners
- the final table shows the HCD expenditures and value added to homes for our optimal threshold of 20% and a default threshold of 50%. The 50% threshold saves HCD money in marketing, but the value added to homes is also quite low. At a 20% threshold, HCD spends $527,800 in marketing and tax credits, which lead to a $1,023,000 increase in the value of the homes
```{r thresholds, message=FALSE, warning=FALSE}

whichThreshold_hcd <- 
  whichThreshold %>% 
  group_by(Threshold) %>% na.omit() %>%
  summarize(HCD_Expenditure = sum(HCD_Expenditure),
            Home_Value_Added = sum(Home_Value_Added))

ggplot(whichThreshold_hcd)+
  geom_line(aes(x = Threshold, y = HCD_Expenditure, color = "HCD_Expenditure"))+
  geom_line(aes(x = Threshold, y = Home_Value_Added, color = "Home_Value_Added"))+
  labs(title = "Model HCD expense and Home value addition By Threshold \nFor Test Sample", y = "Dollars")+theme(legend.title = element_blank())

whichThreshold_revenue <- 
  whichThreshold %>% 
  group_by(Threshold) %>% na.omit() %>%
  summarize(Revenue = sum(Revenue))

ggplot(whichThreshold_revenue)+
  geom_line(aes(x = Threshold, y = Revenue))+
  geom_vline(xintercept =  pull(arrange(whichThreshold_revenue, -Revenue)[1,1]))+
  labs(title = "Home Value Aded Minus HCD Expenditures By Threshold For Test Sample",
       subtitle = "Vertical Line Denotes Optimal Threshold")

whichThreshold_credits <- 
  whichThreshold %>% 
  group_by(Threshold) %>% 
  summarize(Number_Credits= sum(Number_Credits))

ggplot(whichThreshold_credits)+
  geom_line(aes(x = Threshold, y = Number_Credits))+
  labs(title = "Model Number of Credits By Threshold For Test Sample")



# Optimal Threshold
optimum_threshold <- pull(arrange(whichThreshold_revenue, -Revenue)[1,1])

opt <- 
  whichThreshold %>% 
  group_by(Threshold) %>% 
  summarize(HCD_Expenditure = sum(HCD_Expenditure),
            Home_Value_Added = sum(Home_Value_Added),
            Number_Credits= sum(Number_Credits)) %>%
  filter(Threshold == optimum_threshold)

fifty_thresh <-
  whichThreshold %>% 
  group_by(Threshold) %>% 
  summarize(HCD_Expenditure = sum(HCD_Expenditure),
            Home_Value_Added = sum(Home_Value_Added),
            Number_Credits= sum(Number_Credits)) %>%
  filter(Threshold > .499 & Threshold < .51)

final <- data.frame(rbind(opt, fifty_thresh))

kable(final,
      caption = "Optimum Threshold and 50% Threshold") %>% kable_styling()

```

# Conclusion
Should this model be put into production? What could make the model better? What would you do to ensure that the marketing materials result in a better response rate?
- model has low sensitivty. HCD could save money on marketing with increased sensitivity.
- maybe add more demographic information to the model?